Redundancy analysis for hypertension

### 2019-08-07 articletwo.Rmd
Renaming

```{r maaslin means}
pseq.genus.core.pruned.table <- pseq.genus.core.pruned %>%
    prune_taxa(c("g_Adlercreutzia", "g_Anaerotruncus", "g_Sutterella"), .) %>%
    transform(transform = "compositional") %>%
    psmelt %>%
    mutate(map_groups = relevel(factor(dplyr::ntile(MAP, 3)), ref='1'),
           systm_groups = relevel(factor(dplyr::ntile(SYSTM, 3)), ref='1'),
           Abundance = myscale(Abundance))

@@

rbind(table_bp_abund(pseq.genus.core.pruned.table, "map_groups"),
             table_bp_abund(pseq.genus.core.pruned.table, "systm_groups")) %>%
    tibble::column_to_rownames("grp") %>%
    t %>%
    as.data.frame %>%
    kable

>>>>

```{r maaslin means}
pseq.genus.core.table <- pseq.genus.core %>%
    prune_taxa(c("g_Adlercreutzia", "g_Anaerotruncus", "g_Sutterella"), .) %>%
    transform(transform = "compositional") %>%
    psmelt %>%
    mutate(map_groups = relevel(factor(dplyr::ntile(MAP, 3)), ref='1'),
           systm_groups = relevel(factor(dplyr::ntile(SYSTM, 3)), ref='1'),
           Abundance = myscale(Abundance))

@@

rbind(table_bp_abund(pseq.genus.core.table, "map_groups"),
             table_bp_abund(pseq.genus.core.table, "systm_groups")) %>%
    tibble::column_to_rownames("grp") %>%
    t %>%
    as.data.frame %>%
    kable

### 2019-08-07 maaslinruns.Rmd
Renaming

```{r my variables}
var.BP <- c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")
var.CL.min <- c("BL_AGE", "SEX")
var.CL.add <- c("SEX", "BMI", "CURR_SMOKE", "Q57X", "DIAB",
            "BL_USE_RX_C03","BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
```

>>>>

```{r my variables}
var.BP <- c("MAP", "SYSTM", "DIASM", "PULSEPRESSURE", "HYPERTENSION")
var.CL.min <- c("BL_AGE", "SEX")
var.CL.add <- c("SEX", "BMI", "CURR_SMOKE", "Q57X", "PREVAL_DIAB",
            "BL_USE_RX_C03","BL_USE_RX_C07", "BL_USE_RX_C08", "BL_USE_RX_C09")
```

### 2019-08-07 partialrda.Rmd
Renaming

```{r model function}
modelfunction <- function(x,
                          rda.abund,
                          df.meta,
                          modelstr = "rda.abund ~ %s + Condition(%s)",
                          permutations = 1000) {
    covariates <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                   "DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07",
                   "BL_USE_RX_C08", "BL_USE_RX_C09")
    fo <- sprintf(modelstr, x, paste0(covariates, collapse = "+"))
    model <- rda(as.formula(fo), data = df.meta)
    anova.term <- anova(model, by="term", perm=permutations)
    data.frame(var = as.character(x),
               beta = coef(model)[,1][[ifelse(x == "HYPERTENSION", "HYPERTENSION1", x)]],
               conditioned = ifelse("partial.chi" %in% names(summary(model)),
                                        summary(model)$partial.chi,
                                        0),
               constrained = summary(model)$constr.chi,
               unconstrained = summary(model)$unconst.chi,
                p.anova = anova.term[["Pr(>F)"]][1],
               fo = fo)
}
```

@@

```{r rda}
ex.rda <- rda(rda.abundances.species ~ SYSTM + Condition(BL_AGE + SEX + BMI + CURR_SMOKE + Q57X
                                                        + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 +
                                                        + BL_USE_RX_C08 + BL_USE_RX_C09),
              data = meta(pseq.species))
```

>>>>

```{r model function}
modelfunction <- function(x,
                          rda.abund,
                          df.meta,
                          modelstr = "rda.abund ~ %s + Condition(%s)",
                          permutations = 1000) {
    covariates <- c("BL_AGE", "SEX", "BMI", "CURR_SMOKE", "Q57X",
                   "PREVAL_DIAB", "BL_USE_RX_C03", "BL_USE_RX_C07",
                   "BL_USE_RX_C08", "BL_USE_RX_C09")
    fo <- sprintf(modelstr, x, paste0(covariates, collapse = "+"))
    model <- rda(as.formula(fo), data = df.meta)
    anova.term <- anova(model, by="term", perm=permutations)
    data.frame(var = as.character(x),
               beta = coef(model)[,1][[ifelse(x == "HYPERTENSION", "HYPERTENSION1", x)]],
               conditioned = ifelse("partial.chi" %in% names(summary(model)),
                                        summary(model)$partial.chi,
                                        0),
               constrained = summary(model)$constr.chi,
               unconstrained = summary(model)$unconst.chi,
                p.anova = anova.term[["Pr(>F)"]][1],
               fo = fo)
}
```

@@

```{r rda}
ex.rda <- rda(rda.abundances.species ~ SYSTM + Condition(BL_AGE + SEX + BMI + CURR_SMOKE + Q57X
                                                        + PREVAL_DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 +
                                                        + BL_USE_RX_C08 + BL_USE_RX_C09),
              data = meta(pseq.species))
```
